\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-04-20 sections/results.tex
Change: Update results with insights from Figure 7B

  Figure~\ref{fig:figure7}A shows the default network compared against networks generated by altering one of the steps of the pipeline from the default.
  These results indicate that the biggest rewiring in networks occur when the reference database or the network inference algorithm are changed.
  % TODO: Show proof??
  The filtering in the \ac{OP} step when turned off also adds a large number of new nodes, but the edges between the common nodes (with the default network) are fairly conserved.
  % TODO: Finalize this figure
  Furthermore, the L1 distance of networks generated by altering one of the steps of the pipeline from the default against the default network (Figure~\ref{fig:figure7}B) shows that the biggest deviations from the default network occur when the \ac{ta} and \ac{ni} steps are changed, reinforcing the same results observed in Figure~\ref{fig:figure2}.
  Figure~\ref{fig:figure7} shows the co-occurrence networks inferred for the healthy subjects (control) and autistic subjects in the fecal microbiome transplant study~\cite{Kang2017}.
  These consensus networks were generated using the default tools and parameters from Table~\ref{tab:default_options}.

>>>>

  Figure~\ref{fig:figure7}A shows the default network compared against networks generated by altering one of the steps of the pipeline from the default.
  These results indicate that the biggest rewiring in networks occur when the reference database or the network inference algorithm are changed.
  % TODO: Show proof??
  The filtering in the \ac{OP} step when turned off also adds a large number of new nodes, but the edges between the common nodes (with the default network) are fairly conserved.
  Furthermore, the L1 distance of networks generated by altering one of the steps of the pipeline from the default against the default network (Figure~\ref{fig:figure7}B) shows that the biggest deviations from the default network occur when the \ac{ni} steps are changed.
  This result is different from that observed in Figure~\ref{fig:figure2} since in this particular analyses all the steps other than the \ac{ni} step have the consensus algorithm applied to them, which drastically reduces the edges in the graph that have lower probabilities.
  This result reinforces the importance of the consensus network in increasing the robustness of the inferred networks to different processing methods.
  Figure~\ref{fig:figure7}C shows the co-occurrence networks inferred for the healthy subjects (control) and autistic subjects in the fecal microbiome transplant study~\cite{Kang2017}.
  These consensus networks were generated using the default tools and parameters from Table~\ref{tab:default_options}.
